A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-04 latex/main.tex
Updates from Overleaf

It is challenging to accurately reconstruct global events
when there are regions with poor sampling and
jurisdictions with long delays
before sequences become publicly
available \cite{Lancet2021,Kalia2021,Chen2022}.
For example, revisiting the ARG topology periodically
(e.g., rewinding the ARG a month and repeating
with samples that became available later)
might improve the accuracy of the genealogy.

>>>>

It is challenging to accurately reconstruct global events
when there are regions with poor sampling and
jurisdictions with long delays
before sequences become publicly
available~\cite{Lancet2021,Kalia2021,Chen2022}.
For example, revisiting the ARG topology periodically
(e.g., rewinding the ARG a month and repeating
with samples that became available later)
might improve the accuracy of the genealogy.
